Lab 2 Final Report: COVID-19 Case Rate vs Population Demographics and Mask Policy

### 2020-12-05 Jackson_Liu_Temlock_Zhang_Lab2_Draft_Report.Rmd
Update Jackson_Liu_Temlock_Zhang_Lab2_Draft_Report.Rmd
update model 3 after conflict

Next, the regression model for model 3 is based on the existing work from model 2. Two additional variables discussed in Model 3 will be introduced as maximalist approach. The first variable is the "mask_public_bool" (whether the state enforced public mask mandate or not) that represents the policy effects. The second variable introduced is "population_density" (the value is logged as discussed earlier) which is considered an important factor considering nature of spread in disease.

>>>>

Next, the regression model for model 3 is created based on the existing work from model 2. Two additional variables discussed in Model 3 will be introduced as maximalist approach. The first variable is the "mask_public_bool" (whether the state enforced public mask mandate or not) that represents the policy effects. The second variable introduced is "population_density" (the value is logged as discussed earlier) which is considered an important factor related to the spread of disease.
